Predictors of frog survival following translocations - primary analyses

### 2024-08-03 code/translocation_survival_analysis.Rmd
Change plot identifiers to lower case bold font

```{r}
library(tidyverse)
library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)
library(lubridate)

@@

p_elev <- d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = elevation)) + 
          geom_ribbon(aes(ymin = lower, ymax = upper), fill= "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          labs(x = "Elevation of recipient site (meters)", y = "P(1-year survival)") +
          annotate(geom = "text", x = 2500, y = 0.94, label = "B", size = 4) +
          theme_classic()

@@

p_snowt1 <- d1_snowt1z %>% 
  select(site_id, translocation_id, snowt1_z, snow_t1, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(snow_t1) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  ggplot(aes(x = snow_t1)) +
          geom_ribbon(aes(ymin = lower, ymax = upper), fill = "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          labs(x = "Winter severity in year t+1\n(% of average snow depth)", y = "P(1-year survival)") +
          annotate(geom = "text", x = 157, y = 0.92, label = "A", size = 4) +
          theme_classic()

@@

p_sex <- d1_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = male, y = surv)) +
    geom_boxplot(aes(y = .epred, x = sex), fill = "lightgray") +
    labs(x = "Sex", y = "P(1-year survival)") +
    annotate(geom = "text", x = 0.4, y = 0.94, hjust = -1, label = "D", size = 4) +
    theme_classic()

@@

p_donor <- d1_donor %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  ggplot(aes(x = donor, y = surv)) +
    geom_boxplot(aes(y = .epred, x = donor), fill = "lightgray") +
    labs(x = "Donor population", y = "P(1-year survival)") +
    annotate(geom = "text", x = 3.3, y = 0.94, hjust = 0, label = "C", size = 4) +
    theme_classic()

>>>>

```{r}
library(tidyverse)
#library(brms)
library(rstanarm)
library(bayesplot)
library(tidybayes)
library(loo)
library(broom.mixed)
library(janitor)
library(patchwork)
library(lubridate)

@@

p_elev <- d1_elevz %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, elevation, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(elevation) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  # ggplot(aes(x = elevation)) + 
  #         geom_ribbon(aes(ymin = lower, ymax = upper), fill= "lightgray", alpha = 1) +
  #         geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
  #         labs(x = "Elevation of recipient site (meters)", y = "P(1-year survival)") +
  #         annotate(geom = "text", x = 2500, y = 0.94, label = "b", size = 4, fontface = "bold") +
  #         theme_classic()
  ggplot(aes(x = elevation)) + 
          geom_ribbon(aes(ymin = lower, ymax = upper), fill= "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          coord_cartesian(ylim = c(0, 1.0)) +
          labs(x = "Elevation of recipient site (meters)", y = "P(1-year survival)") +
          annotate(geom = "text", x = 2400, y = 1, label = "b", size = 4, fontface = "bold") +
          theme_classic()

@@

p_snowt1 <- d1_snowt1z %>% 
  select(site_id, translocation_id, snowt1_z, snow_t1, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 1000, re_formula = NA) %>% 
  group_by(snow_t1) %>%
  summarise(lower = quantile(.epred, alpha), 
            upper = quantile(.epred, 1 - alpha),  
            median = quantile(.epred, 0.5)) %>%
  # ggplot(aes(x = snow_t1)) +
  #         geom_ribbon(aes(ymin = lower, ymax = upper), fill = "lightgray", alpha = 1) +
  #         geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
  #         labs(x = "Winter severity in year t+1\n(% of average snow depth)", y = "P(1-year survival)") +
  #         annotate(geom = "text", x = 157, y = 0.92, label = "a", size = 4, fontface = "bold") +
  #         theme_classic()

  ggplot(aes(x = snow_t1)) +
          geom_ribbon(aes(ymin = lower, ymax = upper), fill = "lightgray", alpha = 1) +
          geom_line(aes(y = median), color = "blue", linewidth = 1, alpha = 1) +
          coord_cartesian(ylim = c(0, 1.0)) +
          labs(x = "Winter severity in year t+1\n(% of average snow depth)", y = "P(1-year survival)") +
          annotate(geom = "text", x = 7, y = 1, label = "a", size = 4, fontface = "bold") +
          theme_classic()

@@

p_sex <- d1_malec %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, sex, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  # ggplot(aes(x = male, y = surv)) +
  #   geom_boxplot(aes(y = .epred, x = sex), fill = "lightgray") +
  #   labs(x = "Sex", y = "P(1-year survival)") +
  #   annotate(geom = "text", x = 0.4, y = 0.94, hjust = -1, label = "d", size = 4, fontface = "bold") +
  #   theme_classic()
  ggplot(aes(x = male, y = surv)) +
    geom_boxplot(aes(y = .epred, x = sex), fill = "lightgray") +
    coord_cartesian(ylim = c(0, 1.0)) +
    scale_x_discrete(labels = c("female", "male")) +
    labs(x = "Sex", y = "P(1-year survival)") +
    annotate(geom = "text", x = 0.15, y = 1, hjust = -1, label = "d", size = 4, fontface = "bold") +
    theme_classic()

@@

p_donor <- d1_donor %>% 
  select(site_id, translocation_id, snowt1_z, elev_z, male_c, donor, surv) %>% 
  add_epred_draws(m1d_reduce, ndraws = 100, re_formula = NA) %>% 
  # ggplot(aes(x = donor, y = surv)) +
  #   geom_boxplot(aes(y = .epred, x = donor), fill = "lightgray") +
  #   labs(x = "Donor population", y = "P(1-year survival)") +
  #   annotate(geom = "text", x = 3.3, y = 0.94, hjust = 0, label = "c", size = 4, fontface = "bold") +
  #   theme_classic()
  ggplot(aes(x = donor, y = surv)) +
    geom_boxplot(aes(y = .epred, x = donor), fill = "lightgray") +
    coord_cartesian(ylim = c(0, 1.0)) +
    labs(x = "Donor population", y = "P(1-year survival)") +
    annotate(geom = "text", x = 0.5, y = 1, hjust = 0, label = "c", size = 4, fontface = "bold") +
    theme_classic()
